---
output: 
  github_document:
    df_print: "kable"
editor_options: 
  chunk_output_type: console
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
) 
```

# exercism-solutions

<!-- badges: start -->
<!-- badges: end -->

```{r, echo = FALSE}
get_root_dirs <- function(path) {
  dirs <- list.dirs(path, recursive = FALSE)
  dirs <- sub("^./", "", dirs)
  dirs <- dirs[!startsWith(dirs, ".")]
  dirs  
}

get_image <- function(lang) {
  paste0("./.logos/", lang, ".png")
}

get_n_exercises <- function(lang) {
  dirs <- get_root_dirs(lang)
  # pharo-smalltalk has the image in that directory
  dirs <- dirs[!grepl("pharo-smalltalk/pharo-", dirs)]
  length(dirs)
}

make_link <- function(lang) {
  glue::glue('<a href="./{lang}/">{lang}</a>')
}

dirs <- get_root_dirs(".")

md_logo <- function(lang) {
  # glue::glue("![]({get_image(lang)})")
  glue::glue("<img height='40px' src='{get_image(lang)}'></image>")
}
langs <- dplyr::tibble(
  logo = sapply(dirs, md_logo),
  language = sapply(dirs, make_link),
  exercises = sapply(dirs, get_n_exercises)
) |> 
  dplyr::arrange(desc(exercises)) |> 
  as.data.frame()

# dplyr::tibble(
#   logo = dirs,
#   language = sapply(dirs, make_link),
#   exercises = sapply(dirs, get_n_exercises),
#   bar = exercises
# ) |>
#   dplyr::mutate(language = purrr::map(language, gt::html)) |>
#   dplyr::arrange(desc(exercises)) |>
#   gt::gt(caption = glue::glue("Last compiled: {Sys.Date()}")) |>
#   gt::text_transform(
#     locations = gt::cells_body(columns = logo),
#     fn = function(x) {
#       gt::local_image(
#         filename = get_image(x),
#         height = 50
#       )
#     }
#   ) |>  
#   gtExtras::gt_plt_bar(column = bar, keep_column = FALSE) |>
#   gt::cols_label(.list = list(logo = "", language = "", exercises = "", bar = ""))
```

These are my completed solutions to [Exercism](https://exercism.org/) problems. 

I completed the [#12in23](https://exercism.org/challenges/12in23) challenge by
solving 5 non-trivial exercises in each of 12 languages, plus several more.

I am also completing the [#48in24](https://exercism.org/challenges/48in24) challenge.

Total number of languages explored:  <span style="font-size:150%"><b>`r nrow(langs)`</b></p>

Total number of exercises completed:  <span style="font-size:150%"><b>`r sum(langs$exercises)`</b></p>

## Number of Exercises Completed per Language 

```{r, echo = FALSE}
langs
```